
%% 工学システム学類 20xx年度のスタイルファイルです．

%%
%%  platex2e用 (TeX Live 2019 で使えます)
%%  (Overleaf / compiler = pdflatex でも使えます)
%%
% このファイルは，筑波大学工学システム学類の卒業研究論文本体の
% 例を作成するために作ったものです．このファイルを書き換えて，
% この例と同じような書式の卒業論文本体をLaTeXを使って作成する
% ことができます．
% document class はどれか一つを選んで%を外してください

%% document class 
%---
% platexを使う場合
%\documentclass[twoside,twocolumn,a4j,dvipdfmx]{jarticle}
%---
% uplatexを使う場合
%\documentclass[twoside,twocolumn,a4j,dvipdfmx]{ujarticle}
%---
% lualatexを使う場合
% \documentclass[twoside,twocolumn,a4j]{ltjarticle}
%---
% pdflatexを使う場合
\documentclass[uplatex,ja=standard,oneside,twocolumn,a4j,dvipdfmx]{bxjsarticle}

%% packages
% 工学システム学類
\usepackage{esys-thesis}
% 図のファイルを貼り付けるためのパッケージ．
\usepackage{graphicx}
% 用紙マージン
\usepackage{geometry}
\geometry{top=25truemm,bottom=25truemm,left=25truemm,right=25truemm}
%
\usepackage{latexsym}
\usepackage{amsmath, mathtools} % 数式用
\usepackage{amssymb} % \mathbb 用

\usepackage{bm} % ベクトル表記用
\usepackage{siunitx} % 単位用

% 図を並べて表示用
\usepackage[hang,small,bf]{caption}
\usepackage[subrefformat=parens]{subcaption}
\captionsetup{compatibility=false}
% 図の罫線を太く
\usepackage{array}
% サブキャプションの参照にかっこをつける
\captionsetup[subfigure]{labelformat=simple}
\renewcommand{\thesubfigure}{(\alph{subfigure})}

%%%%%% ここから論文内容 %%%%%%
%
% 次の行には，000000の代わりに自分の学籍番号を，KOUSHISUの
% 代わりに大文字のローマ字で自分の名字を例にならって書いて
% 下さい．
%
\pagestyle{plain}

%
% 題目を書いて下さい
%
\title{{\Large 制御可能な動作生成のための条件付き残差学習} \\ {\large Conditional Residual Learning for Controllable Motion Generation}}
%
% 著者名，著者名のローマ字表記，指導教員名を例にならって書い
% て下さい
%
\author{{\Large 水谷 圭 } \\ MIZUTANI Kei \\ (指導教員  境野 翔)}

%
% 卒業論文の概要を書いて下さい
% 本体が日本語なら概要は英語
% If the mainbody is in English, abstract should be in Japanese
%
\eabstract{%
    Bilateral control-based imitation learning (BCIL) enables high-quality robot demonstrations that include both position and force information.
    However, when task conditions change---such as variations in object size, material, or desired placement---new demonstrations must be collected and the model must be retrained from scratch.
    This paper proposes a framework in which a user specifies a numerical label $\boldsymbol{c}$ (the difference between the target and current output) and the robot autonomously executes a trajectory that deviates from a base trajectory by the desired displacement, without any retraining.
    Our central hypothesis is that predicting only the residual $\Delta\xi$ between the corrected and base trajectories, rather than the full trajectory, yields a stronger linear and monotone relationship between the label and the resulting motion---a property required for stable convergence via iterative learning control (ILC).
    Training data for the residual neural network (NN) are collected efficiently using Motion ReTouch, a post-editing technology based on four-channel bilateral control.
    To test this hypothesis, we conduct a preliminary experiment on a pick-and-place task.
    Three models are compared: a direct prediction model (\texttt{direct}), a residual prediction model (\texttt{res}), and a lightweight image-free residual model (\texttt{res\_nonImage}).
    Results show that \texttt{res} achieves $R^2 \approx 0.87$ and Spearman $\rho \approx 0.94$, supporting the hypothesis.
    At the same time, systematic offset at label $\boldsymbol{c} = \boldsymbol{0}$ and label-correlated orientation changes are identified as remaining challenges.
}

\begin{document}

\maketitle
\thispagestyle{plain}


% 序論
\input{sections/Introduction.tex}
% 関連研究
\input{sections/RelatedWorks.tex}
% 提案手法
\input{sections/ProposedMethod.tex}
% 予備実験
\input{sections/Experiment.tex}
% 実験結果と考察
\input{sections/Results.tex}
% まとめ
\input{sections/Conclusion.tex}

% 参考文献
\bibliography{references} %author.bibから拡張子を外した名前
\bibliographystyle{junsrt} %参考文献出力スタイル

\end{document}